---
title: "What's a Fireplace Worth"
author: "=====> Your Name Here <===="
date: "`date()`"
output: html_document
---

<!-- Boilerplate ----------------------------->
```{r include=FALSE}
library(YourCourse) 
```
```{r echo=FALSE,results='asis'}
cat("Rmd source for this document: ")
includeSourceDocuments()
```
<!-- Keep this line and the preceeding ones. -->

You're a homeowner.  You're thinking of renovating your home to add a fireplace. This is very expensive, but you figure it will increase the value of the home and you'll get the money back when you sell the home.

Your problem in this activity is to make a sensible estimate of the amount by which a fireplace would increase the sales price of your house.  This estimate will guide your decision about how much it's worth paying for a fireplace.

You have collected some data on recent house sales in your area.
```{r}
Houses <- our_file("SaratogaHouses.csv")
```
The variables are:

* `Price` the selling price of the house
* `Living.Area` the area of the house in square feet
* `Baths` the number of bathrooms in the house
* `Bedrooms` the number of bedrooms in the  house
* `Fireplace` whether or not the house has a fireplace
* `Acres` the lot size, in acres
* `Age` how old the house is

Your house has a living area of 1500 sq feet, 1.5 bathrooms, 2 bedrooms, a lot of 0.5 acres, and is 25 years old.
