---
title: "What's a Fireplace Worth"
author: "=====> Your Name Here <===="
date: "`date()`"
output: html_document
---

<!-- Boilerplate ----------------------------->
```{r include=FALSE}
library(YourCourse) 
```
```{r echo=FALSE,results='asis'}
cat("Rmd source for this document: ")
includeSourceDocuments()
```
<!-- Keep this line and the preceeding ones. -->

You're a homeowner.  You're thinking of renovating your home to add a fireplace. This is very expensive, but you figure it will increase the value of the home and you'll get the money back when you sell the home.

Your problem in this activity is to make a sensible estimate of the amount by which a fireplace would increase the sales price of your house.  This estimate will guide your decision about how much it's worth paying for a fireplace.

You have collected some data on recent house sales in your area.
```{r}
Houses <- our_file("SaratogaHouses.csv")
```
The variables are:

* `Price` the selling price of the house
* `Living.Area` the area of the house in square feet
* `Baths` the number of bathrooms in the house
* `Bedrooms` the number of bedrooms in the  house
* `Fireplace` whether or not the house has a fireplace
* `Acres` the lot size, in acres
* `Age` how old the house is

Your house has a living area of 1500 sq feet, 1.5 bathrooms, 2 bedrooms, a lot of 0.5 acres, and is 25 years old.

## Kinds of variables

Which variables are categorical? Which quantitative?

Occasionally, it's useful to treat a number as a categorical variable, e.g. Likert scales, quintiles, etc.

Some examples:
```{r}
max( price ~ as.factor(Bedrooms), data=Houses)
max( price ~ ntiles(LivingArea, 5), data=Houses)
```


## Mean prices

* Compare the mean prices of houses with and without fireplaces.
```{r}
# Your R statements here.
```

* Give a simple interpretation of the difference in means.

* Make an informative graphic that compares prices with and without fireplaces.

```{r}
# Your graphics instructions here
```

## Hypothesis testing the difference in means

Carry out a formal hypothesis of the difference between the means for house with and without fireplaces. In addition to giving confidence intervals or standard errors or p-values or the like, give a reasonable interpretation, in words, of your results.

## Distributions

Look at the distribution of house price in the Saratoga data. Explain why the *median* price might be more informative than the mean.

Then, look at the median price 

* for houses with fireplaces and not
* for different numbers of bedrooms 
* for different numbers of bathrooms 
* for different amount of living area

## Transformations

Alternatively, you might look at the logarithm of the price of houses.

Show the distribution of `log10(price)`



## Covariates

You don't really believe that a fireplace adds so much to the price of a house.  Explain what other variables might be playing a role in setting the price.


LIST THEM HERE


Variables that you think play a role but aren't of direct interest --- you're interested in fireplaces after all --- are called *covariates*.
