---
title: "Airplane Flights"
author: "Your Name Here"
date: ""
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  pdf_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---


```{r include=FALSE}
require(mosaic)
require(knitr)
```

###Create Hypothesis

1.  State your null and alternative hypothesis

2.  Gather data (read in data from file)

```{r}
flights<-read.csv("http://mathcs.muhlenberg.edu/~davidson/Datasets/Flights.csv")
head(flights)
```

3.  Look at data.  Create histograms and boxplots of your data.

```{r}
#Create histogram
#Create boxplot

```

4.  Look at numerical summaries of data.

```{r}
#Conduct numerical summaries here


```

5.  According to the graphs and numerical summaries, what are your initial thoughts about the flight lenghts of the airplanes?

6.  We want to run an ANOVA, but need to check our assumptions.  Check the two assumptions here (use R chunk if needed).

```{r}
#Check assumptions for ANOVA (there are two of them you need to check)


```

7.  Our assumptions should NOT be met.  Which assumption is violated?

8.  We'll go ahead and run the ANOVA test for practice, but we must realize that we can't put a lot of faith in the results as we're violating some assumptions.

```{r}
#Practice running an ANOVA test


```

9.  According to our output, what is our conclusion to the ANOVA test?  (Use a standard alpha of 0.05)

10.  What is our estimate for standard deviation? 

```{r}
#sqrt(MSE) = sqrt(Mean Sq Resituals)


```

11. Is our estimate of the pooled standard deviation (SD of the model) close to the standard deviations we found using favstats?

12.  What is the $R^2$ value?  

```{r}
#(Sum Sq Plane)/(Sum Sq Plane + Sum Sq Residuals)


```

13.  Based on our ANOVA model, should we run a multiple comparisons test?  How do you know?

14.  If you should run a multiple comparisons test, run one here:

```{r}
#Run multiple comparisons test here


```

15.  We'll use an alpha level again of 0.05, what are our conclusions based on the multiple comparisons test?

16.  We can write the 4 types of planes as:

N   F  O  W


If we were to draw a box around the planes that are not significantly different - which planes would we draw a box around?

17.  There is really only ONE plane that is significantly different than all other planes according to this test - which plane "is not like the others"?




