---
title: "T-Test Extravaganza Speed Dating"
author: ""
date: "October 2014"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  pdf_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---


```{r include=FALSE}
require(mosaic)
trellis.par.set(theme=theme.mosaic())  
require(knitr)
```


###Instructions.

Use the SpeedDating data to answer the following questions.  For each, state:

1.  The hypothesis (null and alternative)
2.  Which test you are using (one sample t-test, matched pairs, two-sample t-test)
3.  If the assumptions are met for each test
4.  Run the test
5.  State your conclusion in terms of the story.

###Reading in Data

```{r}
speed<-read.csv("http://mathcs.muhlenberg.edu/~davidson/Datasets/SpeedDating.csv")
head(speed)
```

###Question 1

Does attractiveness affect the desire to date?  Compare the means of AttractiveM (if the male thinks the female is attractive) with their decision to date again (DecisionM).

1.  State the null and alternative hypothesis
2.  Which test you are using (one sample t-test, matched pairs, two-sample t-test)?
3.  Are the assumptions met for this test?
4.  Run the test
5.  State your conclusion in terms of the story.


###Question 2

Is there a mutual feeling of shared interests between men and women?  Compare the means of SharedInterestsM to SharedInterestsF to see if there is a significant difference between the means.  (Hint:  think of the "couple" as being asked the same question twice)

1.  State the null and alternative hypothesis
2.  Which test you are using (one sample t-test, matched pairs, two-sample t-test)?
3.  Are the assumptions met for this test?
4.  Run the test
5.  State your conclusion in terms of the story.


###Question 3

On average, do females like their dates?  Compare LikeF to a mean of 5 (assuming 5 is neither like nor dislike).  (Hint:  think about what you want your alternative to be if you want to show females like their dates)

1.  State the null and alternative hypothesis
2.  Which test you are using (one sample t-test, matched pairs, two-sample t-test)?
3.  Are the assumptions met for this test?
4.  Run the test
5.  State your conclusion in terms of the story.
