---
title: "Bone Density"
author: "Your Name Here"
date: 
output: html_document
---

```{r message=FALSE, warning=FALSE}
library(knitr)
library(mosaic)
library(ggplot2)
library(lattice)
```

An experiment was done to compare the bone density of different groups of rats: a control group, a low jump group and a high jump group.  They are interested in seeing if the jumping height has any effect on the bone density in these rats.

###Hypothesis Test

State your hypothesis for this test

###Read in data

```{r}
jump<-read.csv("http://mathcs.muhlenberg.edu/~cha/statistics/datasets/chap12/jumping.txt", sep="\t", header=T)
head(jump)
names(jump)
```

###Graph Data

```{r fig.height=3}
#Create Histograms and Boxplots of the data
```

###Assumptions

```{r fig.height=3}
#Check assumptions with qqplots and favstats (see SD)
```

There are some outliers, especially in the control group, so we want to take the interpretations/results with a grain of salt.  

###ANOVA model

```{r}
#Run the ANOVA model


```

What are the conclusions to the ANOVA model?

What is the SD for the model? (MSE)

```{r}
#Calculate SD (MSE)

```


What is the R^2 value and what does it mean in terms of this problem?

```{r}
#Calculate R^2 value

```


Do you need to run a multiple comparisons test?  How do you know?

If you need to run the multiple comparison tests, run it now and state your conclusions.

```{r}
#Run multiple comparisons test

```



