---
title: "Shapes Analysis"
author: "Allison Davidson"
date: "Tuesday, October 21, 2014"
output: html_document
---

```{r include=FALSE}
library(knitr)
library(mosaic)
```

###State Hypothesis

We want to see if the second time playing you do better/faster.

Ho:  diff=0
Ha:  diff>0

###Read in data

```{r}
shapes<-read.csv("http://mathcs.muhlenberg.edu/~davidson/Datasets/Shapes.csv")
head(shapes)
```

###Look at data

```{r}
histogram(~Time1+Time2, data=shapes, fit="normal")
```

###Create a column called "diff"

```{r}
shapes<-transform(shapes, diff=Time1-Time2)
head(shapes)
```

###Check assumptions (diff approximately normal)

```{r}
histogram(~diff, data=shapes)
favstats(~diff, data=shapes)
xqqmath(~diff, data=shapes)
```

###Since assumptions satisfied, run t-test

```{r}
t.test(~diff, data=shapes)
```

When drawing conclusions, remember to divide p-value by 2 for one sided test and remember the 2 parts of every conclusion.  


###State Hypothesis

Here we want to see if you are faster with all the same color as opposed to all different colors

Ho:  diff=0 (where diff = same-different)
Ha:  

What is alternative hypothesis?

###Look at data

```{r}
#Create a histogram of SameCTime and DiffCTime (where SameCTime is the time to complete the puzzle with the same color and DiffCTime is the time to complete the puzzle with different colors)


```

###Create a column called "diff"

```{r}
shapes<-transform(shapes, diff2=SameCTime-DiffCTime)
head(shapes)
```

###Check assumptions (diff approximately normal)

```{r}
#Create a histogram and qqplot of "diff2" to check for normality.  Also, check the favstats of diff2 to see the mean/sd.



```

###Since assumptions satisfied, run t-test

```{r}
#Run t.test for matched pairs here


```

When drawing conclusions, remember to divide p-value by 2 for one sided test and remember the 2 parts of every conclusion.  

Why don't you get a significant difference?  Why was it important to randomize which type of puzzle you do first (all same color or different colors)?